\chapter*{Conclusion}
\addcontentsline{toc}{chapter}{Conclusion}

\thispagestyle{noheader}

Through this project, we have gained valuable insights and practical experience in applying machine learning techniques to real-world cybersecurity challenges. We have learned how to preprocess and explore datasets, extract meaningful features, and train models for accurate detection of DDoS attacks. Additionally, the development of the application has provided us with hands-on experience in deploying machine learning models for practical use.

Our journey has not only deepened our understanding of machine learning concepts but has also highlighted the importance of collaboration and problem-solving in tackling complex issues such as DDoS attacks. We have learned to approach problems with a systematic and analytical mindset, breaking them down into manageable steps and iteratively refining our solutions.

In addition to advancing our knowledge in machine learning and cybersecurity, this project has also introduced us to new technologies. The integration of FastAPI for the backend and Vue.js for the frontend expanded our technical skill set, allowing us to create a robust and interactive application for our model. 

The process of learning and integrating these technologies was challenging but ultimately rewarding. FastAPI's simplicity and performance made it an ideal choice for building our backend API, while Vue.js's flexibility and reactivity greatly enhanced the user experience of our application.

As we continue our journey in CS and ML, we will carry forward the lessons learned from this project, applying them to future endeavors and contributing to the advancement of these critical fields.